Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-09-25 ms.tex
neatened up the SED plot.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{kic1255_sed.pdf}
\caption{\added{The spectral Energy distribution from VizieR \citep{ochsenbein2000vizieR}.
The photometry is fit in order to estimate the stellar bolometric flux and derive a stellar radius of 0.72 $\pm$ 0.03 R$_\odot$.
We note that the WISE Band 3 and Band 4 excess may arise from a dusty ring or disk of material from the planet, warranting further investigation.}}\label{fig:SED}
\end{centering}
\end{figure*}
}.

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{kic1255_sed.pdf}
\caption{\added{The spectral Energy distribution from VizieR \citep{ochsenbein2000vizieR}.
The photometry is fit in order to estimate the stellar bolometric flux and derive a stellar radius of 0.72 $\pm$ 0.03 R$_\odot$.
We note that the WISE Band 3 and Band 4 excess at 12$\mu$m and 22 $\mu$m may arise from a dusty ring or disk of material from the planet, warranting further investigation.}}\label{fig:SED}
\end{centering}
\end{figure*}
}.
